Of judges, aliens and total preorders

### 2021-02-24 presentation/1901_3230880_philip_heltweg_presentation.tex
fix: small bugfixes
added gitignore for generated files from vscode

	\insertnote

}

@@

\begin{frame}{Motivation}
    How should a judge change their worldview when presented with new information?  
    \note{
        \begin{itemize}
            \item Example question to motivate
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example \footnote{inspired by \cite{Booth2011}, \cite{Darwiche1997}}}
    \begin{itemize}
        \item The agent is a judge in a murder trial, "John" and "Mary" are suspects
        \item $\Sigma = \{ p, q, r\}$
        \begin{itemize}
            \item p = "John is the murderer"
            \item q = "Mary is the murderer"
            \item r = "The victim is an alien"
        \end{itemize}
        \item  $I_{\Sigma} = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
    \end{itemize} 
    \note{
        \begin{itemize}
            \item NOTE
        \end{itemize}
    }
\end{frame}

@@

    \note{
        \begin{itemize}
            \item definition
        \end{itemize}
    }\include{figures/example-visualisation-scatterplot}
\end{frame}

>>>>

	\insertnote
}

@@

\begin{frame}{Motivation}
    How should a judge change their worldview when presented with new information?  
    \note{
        \begin{itemize}
            \item Beispiel Frage zur Motivation
            \item Unvollständige Information: Kein gesichertes Wissen sondern Glauben und Annahmen aus Zeugenaussagen/Indizien
            \item Inkonsistente Information: Zeugen können lügen, Indizien falsch sein, Informationen können mit dem aktuellen Glauben inkonsistent sein
            \item Keine reine richtig/falsch Frage. Soll neuer Information immer geglaubt werden? Wie sollen Konflikte gelöst werden?
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example \footnote{inspired by Booth and Meyer \cite{Booth2011} and Darwiche and Pearl \cite{Darwiche1997}}}
    \begin{itemize}
        \item The agent is a judge in a murder trial, "John" and "Mary" are suspects
        \item $\Sigma = \{ p, q, r\}$
        \begin{itemize}
            \item p = "John is the murderer"
            \item q = "Mary is the murderer"
            \item r = "The victim is an alien"
        \end{itemize}
        \item  $Int({\Sigma}) = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
    \end{itemize} 
    \note{
        \begin{itemize}
            \item NOTE
        \end{itemize}
    }
\end{frame}

@@

    \note{
        \begin{itemize}
            \item definition
        \end{itemize}
    }
\end{frame}
